---
title: 'TASK 10: Dimensionality reduction and Clustering I'
author: "Tami"
date: "2022-09-01"
output:
  md_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
##TASK 10. Dimensionality reduction and clustering I
##Load the iris dataset
library(tidyverse)
library(dplyr)
data(iris)
```

```{r}
##Convert iris data into unlabelled dataset
df<- iris
dfIris<- select(df, -Species)
```

```{r}
##Check the PCA eligibility
cor(dfIris)
mean(cor(dfIris))
#The variables are eligible for PCA
```


##Formulate two questions or hypotheses on the data, that you want to answer by using a PCA
#1. Check whether the PCs capture the essence of the original variable
#2. Check whether the PCs are independent

```{r}
##Now, let's run PCA
PCA<- princomp(dfIris)
```

```{r}
##Inspect the loadings with the PCA object
PCA$loadings
```

```{r}
##Use the score to check principal components
PCvalues<- PCA$scores
```

```{r}
##Check correlation to see whether they are independent
cor(PCvalues)
```

##The correlation is almost zero, therefore, the variables are independent.

```{r}
##Visualize PCA
#install.packages("ggfortify")
library(ggfortify)
```

```{r}
PCAplot<- autoplot(PCA, data = iris, colour= 'Species')
PCAplot
```

```{r}
##Explain the variances with a scree plot
library(ggplot2)
```

```{r}
##calculate total variance explained by each principal component
var_explained = PCA$sdev^2 / sum(PCA$sdev^2)
```

```{r}
##Create a Scree plot
qplot(c(1:4), var_explained) + 
  geom_line() + 
  xlab("Principal Component") + 
  ylab("Variance Explained") +
  ggtitle("Scree Plot") +
  ylim(0, 1)
```

```{r}
##Investigate potential correlations of your PCs 
biplot(PCA)
```

##Comment what you can see on them and how you interpret the result

```{r}
print(var_explained)
```
##The first principal component explains 92.46% of the total variation in the dataset.
##The second principal component explains 5.31% of the total variation in the dataset.
##The third principal component explains 1.71% of the total variation in the dataset.
##The first principal component explains 0.5% of the total variation in the dataset.