---
title: "TASK 9. Linear Models II"
author: "Tami"
date: "2022-09-01"
output:
  md_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
##TASK 9. Linear Models II
##Linear Mixed Models
##LOad dataset
Takyodt<- read.csv("Tayko.csv")
```

```{r}
#Structure of data
str(Takyodt)
```

##The response variable
#In this data, my response variable is "Spending"

##Run a Linear Mixed Model now.

```{r}
##First, check the independence of observations
#Using the cor() function, test the relationship between independent variables to ensure they are not highly
#correlated.
cor(Takyodt$Freq, Takyodt$last_update_days_ago)
cor(Takyodt$Freq,  Takyodt$X1st_update_days_ago)
cor(Takyodt$Freq, Takyodt$Web.order)
cor(Takyodt$Freq, Takyodt$Gender.male)
cor(Takyodt$Freq, Takyodt$Address_is_res)
cor(Takyodt$Freq, Takyodt$Purchase)
```

#The correlation between the independent variables is small as observed, so we can include the parameters in
#in regression model

```{r}
##Check for Linearity
##The r/ship between the independent and dependent variables must be linear. We can test this visually
#by drawing a scatter plot to see if the distribution of data points is linear
#This can be checked using scatter plots

plot(Spending ~ Freq, main = "A plot of Spending against Frequency", data = Takyodt)
plot(Spending ~ last_update_days_ago, main = "A plot of Spending against last_update_days_ago", data = Takyodt)
plot(Spending ~ X1st_update_days_ago, main = "A plot of Spending against X1st_update_days_ago", data = Takyodt)
plot(Spending ~ Web.order, main = "A plot of Spending against Web.order", data = Takyodt)
plot(Spending ~ Gender.male, main = "A plot of Spending against Gender.male", data = Takyodt)
plot(Spending ~ Address_is_res, main = "A plot of Spending against Address_is_res", data = Takyodt)
plot(Spending ~ Purchase, main = "A plot of Spending against Purchase", data = Takyodt)
```

#Although some relationships are a bit less clear, it still appears linear
#so we can proceed with linear regression.

```{r}
##Now, let's conduct the Linear Mixed Model analysis
regmd<- lm(Spending ~ ., data = Takyodt)
summary(regmd)
```

#From the statistics witnessed in the model, it is evident that some factors have no significant effect #on the  
#amount of spending
#A summary of the factors that have a significant effect on spending are as follows
#The estimated effect of sequence number on spending is -0.004569
#The estimated effect of source u on spending is -2.446
#The estimated effect of Freq on spending is 77.329, which is quite high.
#The estimated effect of last_update_days_ago on spending is -0.0155
#The estimated effect of X1st_update_days_ago on spending is 0.0058
#The estimated effect of Web.order on spending is -3.35
#The estimated effect of Gender.male on spending is -1.587
#The estimated effect of purchase on spending is 92.01, which is quite high


#From the statistics above, frequency and purchase are the leading factors that influence the amount of spending
#For instance, for every 1%  of frequency, there is a 77.329% increase in spending,
#For every 1% of purchase, there is a 92.01% increase in spending,
#The other factors that least affect spending are;
#For every 1% of sequence number, there is 2.446% decrease in spending
#For every 1% of last_update_days_ago, there is 3.35% decrease in spending
#For every 1% of Gender.male, there is 1.587% decrease in spending

```{r}
##Lets now chekc for homoscedacity)
#This involves checking whether the observed data meets our model assumptions.
par(mfrow= c(2,2))
plot(regmd)
par(mfrow= c(1,1))
```
#The residuals show no bias, so the model fits the assumption of homoscedasticity

```{r}
##Let's now predict the models
#Predicting the values of speding based on the linear model
predict01<- predict.lm(regmd, data= Takyodt)
```

#Reporting the results
##From the results of the model, there is a significant relationship between price of vehicles and tax,
#price and engine size since they have a p value of less than 0.005 (p<0.005).

```{r}
##Use the Random Forest Model
library(stats)
library(randomForest)

##Split the data into testing and training 
index<- sample(2, nrow(Takyodt), replace = TRUE, prob = c(0.7, 0.3))
```

```{r}
##Training data
Training<- Takyodt[index==1, ]
```

```{r}
##Testing data
Testing<- Takyodt[index== 2, ]
```

```{r}
##Random Forest Model
RMF<- randomForest(Spending ~., data = Training)
```

```{r}
##Evaluating model accuracy
Spending_pred<- predict(RMF, Testing)
```

```{r}
##Confusion Matrix
CFM<- table(Testing$Spending, Spending_pred)
```

```{r}
##Let's use the Logistic Regression Model
GLM<- glm(Purchase~ ., family = "binomial", data = Training)
summary(GLM)
```
## Which model describes better your data? Explain
#Undoubtedly, Linear Mixed Model describes my data appropriately. This is because I was able to conduct an analysis and clearly understand the effects of corresponsing variables on spending
