---
title: 'TASK 8: Linear Models I'
author: "Tami"
date: "2022-09-01"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

---
title: 'TASK 8: Linear Models I'
author: "Tami"
date: "2022-09-01"
output: word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
##TASK 8. Linear Models I
##Upload the dataset
MarketData<- read.csv("marketing.csv")
```

```{r}
##Check the data types
str(MarketData)
```

##The explanatory variable is sales and the response variable is Youtube

```{r}
##Check whether there is a correlation between the two
cor(MarketData$sales, MarketData$facebook)
```


#Yes, there is a positive correlation of 0.5762 between sales and facebook.

```{r}
library(lmtest)# for function "bptest" and "dwtest"
library(MASS)# to create the histogram of the residuals
```

```{r}
## Run the simple regression model
fit <- lm(sales ~ youtube, data = marketing)
```

```{r}
## summarize the results
summary(fit)
```

```{r}
##Fit the Linear Regression Model
#Check the assumptions
# histogram of the residuals
sresid <- studres(fit)
hist(sresid, freq=FALSE,
     main="Distribution of Studentized Residuals")
xfit<-seq(min(sresid),max(sresid),length=40)
yfit<-dnorm(xfit)
lines(xfit, yfit)
#The histogram looks like a bell-curve. Therefore,residuals might be normally distributed 
```


```{r}
##QQ-plot of the residuals
qqnorm(resid(fit), col = "darkgrey")
qqline(resid(fit), col = "dodgerblue", lwd = 2)
 ##Because the vast majority of points on or very near the line, the residuals may be normally distributed.
```

```{r}
shapiro.test(resid(fit))
##The large p-value (i.e., larger than 0.05) indicates the normality of the residuals.
```

```{r}
##homoscedasticity (Non-constant Error Variance)
plot(fitted(fit), resid(fit), col = "grey", pch = 20,
     xlab = "Fitted", ylab = "Residual",
     main = "Fitted versus Residuals")
abline(h = 0, col = "darkorange", lwd = 2)
#The fitted versus residuals plot looks good. We don’t see any obvious pattern, and the variance looks roughly constant. (Maybe a little larger for large fitted values, but not enough to worry about.)
```

```{r}
##Non-independence of residuals using the Durbin-Watson test 
dwtest(fit)
##The large p-value (i.e., larger than 0.05) indicates that residuals are independent
```
##Which Model describes your data well? Explain.
#The model that describes the data well is the linear model because it gives the linear relationship between the two variables in question.

